Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-22 paper.tex
minor edit

This section presents our first contribution, the definition of
hypercoercions.  The design of hypercoercions is motivated by the
observation that a normal coercion has at most three parts;
projections are always at the beginning; injections and failures are
always at the end. Hypercoercions make this structure explicit: a
hypercion either is $\hyperCoercionI$, the identity cast for
$\TOOdyn$, or contains three parts, where the first part is either a
projection or the identity, the last part is either an injection, a
failure, or the identity, and each kind of middle part corresponds to a type 
constructor and include hypercoercion(s) for subpart(s) of corresponding values.
\todo[inline]{What about the middlepart? -JS
\\---\\
Fixed. -KC}

\figref{fig:hypercoercion} defines the syntax of hypercoercions. Types, 
pre-types, and blame labels are as before.

Let $c$ range over hypercoercions. A hypercoercion either is the identity 
cast between the dynamic types, or includes a head, a middle, and a tail. 
Let $h$ range over heads. A head is either a no-op, or a projection.
Let $m$ range over middles. There is a one-to-one 
correspondence between middles and type constructors. 
We generalize shallow-consistency to middles $m \smile m$ in the obvious way.
Let $t$ range over tails. A tail is either a no-op, an injection, or a 
failure.

>>>>

This section presents our first contribution, the definition of
hypercoercions.  The design of hypercoercions is motivated by the
observation that a normal coercion has at most three parts;
projections are always at the beginning; injections and failures are
always at the end. Hypercoercions make this structure explicit: a
hypercion either is $\hyperCoercionI$, the identity cast for
$\TOOdyn$, or contains three parts: the head is either a projection or
the identity, the tail is either an injection, a failure, or the
identity, and the middle involves coercions underneath a type
constructor, i.e., coercions between function, pair, and sum types.

\figref{fig:hypercoercion} defines the syntax of
hypercoercions. Types, pre-types, and blame labels are as before.  Let
$c$ range over hypercoercions. A hypercoercion either is the identity
cast between the dynamic types, or includes a head, a middle, and a
tail.  Let $h$ range over heads. A head is either a no-op, or a
projection.  Let $m$ range over middles. There is a one-to-one
correspondence between middles and type constructors.  We generalize
shallow-consistency to middles $m \smile m$ in the obvious way.  Let
$t$ range over tails. A tail is either a no-op, an injection, or a
failure.
